Identification of Direct Cherenkov Pixels using Boosted Decision Trees

### 2016-05-18 report/bdtarticle.tex
Backup 18/05/16

\section{Image Simulation}
The full simulation of air showers was performed using the CORSIKA package atmospheric profile derived from measurements conducted at the HESS site in Namibia. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi \propto E^{-2.7}$. For each set of simulated event, 4 unique random number seeds were used to generate the shower. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.

@@

\section{DC Pixel Identification}  
As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for a set of test data.   For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut, reducing the number of accepted DC candidates. For each image, the smallest $Q_{DC}$ among any remaining pixels was used to identify as the DC pixel candidate. Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel. In the original analysis, an additional cut $r_{core} \textgreater 40m$ was applied. However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$. Consequently, this particular cut was omitted, along with the Impact Parameter cuts.

@@

The candidates were checked against the true DC pixels identified in the EAS-free images. Of 2000 events it was found that there were 6000 triggered images. Of these images, 17\% passed the required cuts. The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}. These values served as a benchmark for BDT performance.

@@

Application of this combined cut greatly increases the successful identification rate. Of the 2000 events, 84\% of events passed all of the required cuts. The BDT was found to be 90 \% accurate in identifying the DC pixel in those passing events. This represents a very significant improvement in DC pixel identification over the previous QDC method, and corresponds to a fivefold increase in the number of HESS data events that can be studied using the LPD method.

>>>>

\section{Image Simulation}
The full simulation of air showers was performed using the CORSIKA package, with a standard atmospheric profile derived from measurements conducted at the HESS site in Namibia. In total, 2000 training events and a further 2000 testing events were simulated. The simulated particles were $Fe^{56}$, within the Energy Range of $35-135$ TeV and a spectrum $\phi(E) \propto E^{-2.7}$. For each set of simulated event, 4 unique random number seeds were used to generate the shower. An altitude of 1800m was assumed, again corresponding to the HESS site. The simulated zenith angle ranged from $0\degree < \theta < 2 \degree$, while the simulated azimuth angle ranges from $-2\degree < \phi < 2 \degree$. The four smaller HESS-phase-1 telescopes were arranged in a cross along the x/y axis with the larger HESS-phase-2 \textquoteleft CT5' telescope placed at the center. The length of each cross arm was $85m$. The simulated target region of the cores was chosen to be a square centered on CT5, with each 300m-long side bisecting the x/y axis.

@@

\section{DC Pixel Identification}  
As a basis for comparison, the original HESS cuts listed in \ref{tab:table1} were replicated for the set of test data.   For every image, the total image amplitude $I_{tot}$ was used alongside the zenith angle $\theta$ to determine a unique $Q_{DC}$ cut, reducing the number of accepted DC candidates. For each image, the smallest $Q_{DC}$ among any remaining pixels was used to identify as the DC pixel candidate. Because many images had no pixel that passed all cuts, the $Q_{DC}$ method was frequently unable to identify a DC pixel. In the original analysis, an additional cut $r_{core} \textgreater 40m$ was applied. However, the uncertainty in determining the core position through Hillas Analysis is typically of the order of $\pm 30m$. Consequently, this particular cut was omitted, along with the Impact Parameter cuts.

@@

The candidates were checked against the true DC pixels identified in the EAS-free images. Of 2000 testing events it was found that there were 6000 triggered images. Of these images, 5.7\% passed the required cuts. The $Q_{DC}$ was found to be 68\% accurate in identifying the DC pixel in those passing images, as shown in \ref{fig:cutdistribution}. These values served as a benchmark for BDT performance.

@@

Application of this combined cut greatly increases the successful identification rate. Of the 2000 events, 57\% of events passed all of the required cuts. The BDT was found to be 85 \% accurate in identifying the DC pixel in those passing events. This represents a very significant improvement in identification accuracy over the previous QDC method, and corresponds to a fivefold increase in the number of HESS telescope images with corresponding identified DC pixels.
